Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-03-20 thesis.tex
finish info on INLA
adjust preface
mvoe hack into a to do

% Generic maths commands
\def\reals{\mathbb{R}}
\def\nats{\mathbb{N}}
\def\sampSpace{\mathcal{X}}
\def\dist{\sim}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\V}{\mathbb{V}}
\DeclareMathOperator{\I}{\mathbb{I}}
\DeclareMathOperator{\prob}{\mathbb{P}}
\DeclareMathOperator{\p}{\pi}
\DeclareMathOperator{\var}{\mathbb{V}}
\DeclareMathOperator{\indicator}{\mathbb{I}}
\DeclareMathOperator{\cov}{Cov}
\DeclareMathOperator{\cor}{Cor}
\DeclareMathOperator{\logit}{logit}
\DeclareMathOperator{\Ber}{Bernoulli}
\DeclareMathOperator{\Bin}{Binomial}
\DeclareMathOperator{\Poi}{Poisson}
\DeclareMathOperator{\BetaDist}{Beta}
\DeclareMathOperator{\Exponential}{Exponential}
\DeclareMathOperator{\NBr}{NegBin}
\newcommand{\NBc}{\NBr_{c}}
\newcommand{\NBs}{\NBr_{s}}
\DeclareMathOperator{\BB}{BetaBin}
\DeclareMathOperator{\GamDist}{Gamma}
\DeclareMathOperator{\MN}{Multinomial}
\DeclareMathOperator{\N}{N}
\DeclareMathOperator{\LN}{LN}
\DeclareMathOperator{\LKJ}{LKJ}
\DeclareMathOperator{\expit}{expit}
\newcommand\matr{\bm}
\newcommand\set{\mathcal}
\renewcommand{\vec}{\bm}
\newcommand{\ssep}{:}

@@

\title{Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys}
\author{Joshua Blake}
\date{\today}
\subjectline{MRC Biostatistics Unit}
\college{Jesus College}
\collegeshield{CollegeShields/jesus}
% \keywords{one two three}

%% Submission date [optional]:
% \submissiondate{November, 2042}

%% You can redefine the submission notice [optional]:
% \submissionnotice{A badass thesis submitted on time for the Degree of PhD}

@@

@@

\todo[inline]{Mention use of early version of this work in ONS reports}

@@

\todo[inline]{Delete below lines - only here to make compiling individual chapters work}
\cref{perf-test:eq:piu}
\cref{inc-prev:eq:forward-substitute}
\cref{inc-prev:eq:EPt-matrix}
\cref{inc-prev:eq:Smatrix}
\listoftodos

>>>>

% Generic maths commands
\def\reals{\mathbb{R}}
\def\nats{\mathbb{N}}
\def\sampSpace{\mathcal{X}}
\def\dist{\sim}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\V}{\mathbb{V}}
\DeclareMathOperator{\I}{\mathbb{I}}
\DeclareMathOperator{\prob}{\mathbb{P}}
\DeclareMathOperator{\p}{\pi}
\DeclareMathOperator{\var}{\mathbb{V}}
\DeclareMathOperator{\indicator}{\mathbb{I}}
\DeclareMathOperator{\cov}{Cov}
\DeclareMathOperator{\cor}{Cor}
\DeclareMathOperator{\logit}{logit}
\DeclareMathOperator{\Ber}{Bernoulli}
\DeclareMathOperator{\Bin}{Binomial}
\DeclareMathOperator{\Poi}{Poisson}
\DeclareMathOperator{\BetaDist}{Beta}
\DeclareMathOperator{\Exponential}{Exponential}
\DeclareMathOperator{\NBr}{NegBin}
\newcommand{\NBc}{\NBr_{c}}
\newcommand{\NBs}{\NBr_{s}}
\DeclareMathOperator{\BB}{BetaBin}
\DeclareMathOperator{\GamDist}{Gamma}
\DeclareMathOperator{\MN}{Multinomial}
\DeclareMathOperator{\N}{N}
\DeclareMathOperator{\LN}{LN}
\DeclareMathOperator{\LKJ}{LKJ}
\DeclareMathOperator{\expit}{expit}
\newcommand\matr{\bm}
\newcommand\set{\mathcal}
\renewcommand{\vec}{\bm}
\newcommand{\ssep}{:}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\title{Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys}
\author{Joshua Benjamin Blake}
\date{\today}
\subjectline{MRC Biostatistics Unit}
\college{Jesus College}
\collegeshield{CollegeShields/jesus}
% \keywords{one two three}

%% Submission date :
\submissiondate{March 2024}

%% You can redefine the submission notice [optional]:
\submissionnotice{%
    This thesis is submitted for the degree of \\ \emph{Doctor of Philosophy} \\
    March 2024
}

@@

\preface{%
    \todo[inline]{Write preface}
    \begin{itemize}
        \item Early version of this work used in ONS reports
        \item Chapters in JASA paper
        \item Chapter for PNAS (or similar) journal
    \end{itemize}
}

@@

@@

\todo[inline]{
    Equation numbering hack
    \cref{perf-test:eq:piu}
    \cref{inc-prev:eq:forward-substitute}
    \cref{inc-prev:eq:EPt-matrix}
    \cref{inc-prev:eq:Smatrix}
}
\listoftodos
